### 2019-03-07 paper/sex_selection_spacing-ver2.tex
Explain why no first spell analysis

As mentioned above, 8.5\% of women gave birth less than nine months
after they were married, and the first spell, therefore, begins at the 
month of marriage.
The exception is for women married very young, where I use the month they 
turned 12.
The second and subsequent spells begin nine months after the previous birth 
because that is the earliest we should expect to observe a new birth.
A few women report births that occurred less than nine months 
after the previous birth; I drop those women from the sample as mentioned above.

All spells continue until either a child is born or censoring occurs.
Censoring can happen for three reasons:
the survey takes place;
sterilization of the woman or her husband;
or too few births are observed for the method to work.
For the first spell I set censoring because of too few births to 108 months 
(nine years) after marriage,
while for the second, third, and fourth spells censoring is at 96 months 
(eight years) after a birth can occur.
With these cut-offs, less than one percent of observed births occur after
the spell cut-off.%
\footnote{
\input{../tables/num_missed.tex}
Recall also that these numbers are totals across all 36 separate regressions.
}

I group spells into four periods based on the year of marriage
or year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.
The periods follow the main changes in availability and legality of 
prenatal sex determination discussed in the Introduction.
The allocation into periods is determined by when conception and therefore 
decisions on sex selection can begin, even if we do not observe
any births until nine months later.

The allocation into periods means that some spells cover two periods.
A couple may, for example, be married in 1984, but not have their first 
child until 1986.
That couple's first spell will be in the 1972--1984 period, even though 
most of the interval falls in the 1985--1994 period.
Hence, prenatal sex determination was likely available when some
children from spells that began in the 1972--1984 period were conceived,
which could result in evidence of sex-selective abortions even for this
period.
Similarly, a spell that started in the 1985--1994 period may have been partly 
or mostly under the PDNT act.
The effect is a downward bias in the differences between the periods.

>>>>

I focus here on the second through fourth spells, that is, from the second birth until
at most the fourth birth.
The first spell from marriage to the first spell is excluded because of data issues.
In NFHS-1 and NFHS-2 the only information on marriage timing is age at marriage and all
spell durations are therefore imputed.
In NFHS-3 about a third of respondent did not provide complete information on the
timing of marriage and therefore had the length of their first spell imputed using only
the age at marriage.
The result of the imputation is that very large numbers of women end up with very short,
i.e. less than 9 months, or negative spells and that comparing spell duration over time
for the first spell is subject to an excessive amount of noise.

The second and subsequent spells begin nine months after the previous birth 
because that is the earliest we should expect to observe a new birth.
All spells continue until either a child is born or censoring occurs.
Censoring can happen for three reasons:
the survey takes place;
sterilization of the woman or her husband;
or too few births are observed for the method to work.
For all spells censoring is set at 96 months (eight years) after a birth can occur.
With these cut-offs, less than one percent of observed births occur after
the spell cut-off.%
\footnote{
\input{../tables/num_missed.tex}
}

I group spells into four periods based on the year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.
The periods follow the main changes in availability and legality of 
prenatal sex determination discussed in the Introduction.
The allocation into periods is determined by when conception and therefore 
decisions on sex selection can begin, even if we do not observe
any births until nine months later.

The allocation into periods means that some spells cover two periods.
A couple may, for example, have their first child in 1984, but not have their second 
child until 1986.
That couple's second spell will be in the 1972--1984 period, even though 
most of the interval falls in the 1985--1994 period.
Hence, prenatal sex determination was likely available when some
children from spells that began in the 1972--1984 period were conceived,
which could result in evidence of sex-selective abortions even for this
period.
Similarly, a spell that started in the 1985--1994 period may have been partly 
or mostly under the PDNT act.
The effect is a downward bias in the differences between the periods.
